Make any stupid plot you want

### 2021-04-08 draft/sections/intro.tex
moving stuff around + regenerate figures + some words

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/intro/dar.png}
    \caption{Visualization is a mapping from data into visual encodings that are then rendered into images. In our model, this visual encoding stage is called the artist.}
    \label{fig:intro_artist_stages}
\end{figure}

@@

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/intro/artist.png}
    \caption{This table encodes information that here we choose to represent as a map or time series to try to match the visual encoding of the data to the structure inferred from the date and latitute, longitude fields of the dataset.}
    \label{fig:intro_artist_stages}
\end{figure}

@@

\begin{figure}[H]
    \begin{subfigure}{1\textwidth}
        \includegraphics[width=1\columnwidth]{figures/intro/continuity.png}
        \caption{The line plot does not preserve \textit{continuity} because it implies that the discrete records are connected to each other, while the bar plot is \textit{continuity} preserving because it visually represents the records as independent data points. }
        \label{fig:intro:continuity}
    \end{subfigure}
    \begin{subfigure}{1\textwidth}
        \includegraphics[width=1\columnwidth]{figures/intro/equivariance.png}
        \caption{The data in blue is scaled by a factor of two, yielding the data in orange. To preserve \textit{equivariance}, the blue line plot representation of the unscaled data is also scaled by a factor of two, yielding the orange line plot that is equivalent to the scaled data.}
        \label{fig:intro:equivariance}
    \end{subfigure}
  \caption{}
  \label{fig:intro:structure}
  \end{figure}
  The structure that the transformations that make up a visualization library must preserve are \textit{continuity} and \textit{equivariance}, as illustrated in \autoref{fig:intro:structure}.
\begin{mdframed}[roundcorner=10pt, frametitle= definitions, frametitlerule=true, frametitlebackgroundcolor=gray!10]
    \begin{description}
        \item[\textbf{continuity}] How records in the dataset are connected to each other, e.g. discrete rows, neworked nodes, points on a continuous surface
        \item[\textbf{equivariance}] if an action is applied to the data or the graphic--e.g. a rotation, permutation, translation, or rescaling-- there must be an equivalent action applied on the other side of the transformation. 
    \end{description}
\end{mdframed}

  In \autoref{fig:intro:continuity}, the line plot does not preserve continuity because the line connecting the discrete categories implies that the frequency of weather events is sampled from a continuous interval and the categories are points on that interval. In \autoref{fig:intro:equivariance}, the data and visual representation are scaled by equivalent factors of two, resulting in the change illustrated in the shift from blue to orange data and lines.
